Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-29 2016-Weak-FH-Bisim/WeakBisim.tex

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\beta_{j p x y}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
where\\
$
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post\,}\right)$

@@

$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
$\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\

@@

     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\

@@

     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1} \subst{\Post_{OT_x}}  \\

@@

     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)$\\

@@

   ( \forall j\in J_{x y}. \vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} \Big)$\\

@@

\Big(\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post^1}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}}\Big)$\\ 
Finally, the conjunction with the term $\Pred^3\subst{\Post^2}\subst{\Post^1}$ of the both sides of the implication and rewriting, we get:\\
$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\

@@

\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2}
\subst{\Post^1}\subst{\Post_{OT_{x y}}} 
\subst{\Post_{OT_x}} \Big)$\\ 
Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}}\subst{\Post_{OT_x}}$ on the right side of the implication.

@@

$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\!\in\! J_{x y z}. \vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \underbrace{\subst{\Post^3}\subst{\Post^2}
\subst{\Post^1}}_{\subst{\Post_{OT}}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$

@@

\Big(\forall j\in J_{x y z}. \vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$

@@

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta^3_p},\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
$\\

>>>>

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)$\\

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\beta_{j p x y}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\right)$.\\

@@

\begin{lemma}
\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
    \WT>$ be the
weak open automata derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred^2,\Post^2 }
         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha} s'} \in\WT
%}
\end{mathpar}
\TODO{changer alpha...}
where\\
$
s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
$

@@

     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post\,}\right)$

@@

$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2\shortotimes\Post^1}$\\
$\Post_{OT}=\Post^3\subst{\Post^2\shortotimes\Post^1}$\\

@@

     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$\\

@@

     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1\shortotimes\Post_{OT_x}}  \\

@@

     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1\shortotimes\Post_{OT_x}} \right)$\\

@@

   ( \forall j\in J_{x y}. \vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post^1\shortotimes\Post_{OT_x}} \Big)$\\

@@

\Big(\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post^1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 
Finally, the conjunction with the term $\Pred^3\subst{\Post^2\shortotimes\Post^1}$ of the both sides of the implication and rewriting, we get:\\
$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\

@@

\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2\shortotimes \Post^1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.

@@

$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\!\in\! J_{x y z}. \vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$

@@

\Big(\forall j\in J_{x y z}. \vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$

@@

\newpage
\begin{proof} Suppose we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta^3_p},\Pred\,^3_p, \Post_p^3   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j} }}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=m_1}^{0}\Post_j^1}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j}\Big)\\
\Post=\bigotimes_{j=m_2}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j$

------------------------

$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
$\\
